Compiling refinement types to dependent types

### 2020-07-11 tex/paper.tex
Add units to the core language

We take $\lambda C$ \cite{Nederpelt14} enriched with case-splitting inspired by \cite{TAPLVariants,EisenbergThesis} as our core dependently typed language.

@@

\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing}{Sort,Var,Weaken,Form,App,Abs,Conv}
  \caption{Core language typing rules}
  \label{fig:core_typing}
\end{figure}

>>>>

We take $\lambda C$ \cite{Nederpelt14}
enriched with case-splitting inspired by \cite{TAPLVariants,EisenbergThesis}
and a unit type as our core dependently typed language.

@@

\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing}{Sort,UnitType,UnitTerm,Var,Weaken,Form,App,Abs,Conv}
  \caption{Core language typing rules}
  \label{fig:core_typing}
\end{figure}
